Which fifteen-minutes neighborhoods are dead-ends? An analysis of the network attributes of fifteen-minute pedsheds

### 2024-10-21 paper/paper.Rmd
methodology edits

The proposed method involves studying 15-minute walking neighborhoods in two stages. In the first stage, we assess the accessibility levels of Hamilton's watersheds from a normative perspective, focusing on the provision of opportunities. In the second stage, we characterize the topology urban and suburban walksheds based on a set of network structure attributes. Finally, we analyze the effect of walkshed size on urban and suburban networks, and consequently, on access to opportunities.

@@

Finally we

>>>>

The proposed method involves studying 15-minute walking neighborhoods in two stages. In the first stage, we assess the accessibility of Hamilton's walksheds from a normative perspective, focusing on the availability of opportunities. In the second stage, we analyze the topology of urban and suburban walksheds based on various network structure attributes. Finally, we examine whether there are differences in transportation network topology between urban and suburban areas, and analyze how these differences affect access to opportunities within walksheds.

@@

Finally we study effects in accessibility
